Algorithm explanation

### 2013-08-26 article/thesis.tex
Related work separated

One of the most common methods of such abstraction is predicate
abstraction\cite{DBLP:conf/cav/GrafS97} with CounterExample-Guided
Abstraction Refinement (CEGAR) \cite{DBLP:conf/cav/ClarkeGJLV00}.  An
automated theorem prover finds appropriate predicates for every
program location.  An execution states at those locations is then
expressed by a Boolean valuation of the given predicates.  If the
abstraction is too coarse and a model checker discovers an infeasible
error execution path in an abstract system, the prover computes an
additional predicate at those program locations to refine the
abstraction predicates.

In order to obtain an additional abstraction predicate at program
locations along the infeasible counterexample, one class of automated
theorem provers, called an interpolating theorem prover, computes a
separating predicate called an interpolant between two sets of
constraints; the one consists of the constraints from the program
entry point to the location, and the other consists of the constraints
from the location to the program failure.  Those constraints include
variable assignments and assertions to be satisfied originated from
conditional branches.

@@

We incorporated our algorithm to the software model checker for
higher-order programs (MoCHi) \cite{DBLP:conf/pldi/KobayashiSU11}.

@@

Horn clause to interpolation problem.
\cite{DBLP:conf/ppdp/UnnoK09}

CSIsat
\cite{DBLP:conf/cav/BeyerZM08}

FOCI
\cite{website:foci}

CLP-Prover
\cite{website:clp}

We incorporated our algorithm to the software model checker for
higher-order programs (MoCHi) \cite{DBLP:conf/pldi/KobayashiSU11}.

@@

\chapter{Related work}
\label{chap:related}

Lorem ipsum
\cite{DBLP:conf/cav/McMillan03} % Interpolation and SAT-Based Model Checking
\cite{DBLP:conf/popl/HenzingerJMM04} % Abstractions from proofs
\cite{DBLP:journals/tcs/McMillan05} % An interpolating theorem prover
\cite{DBLP:conf/tacas/McMillan05} % Applications of Craig Interpolants in Model Checking
\cite{DBLP:conf/tacas/JhalaM06} % A Practical and Complete Approach to Predicate Refinement
\cite{DBLP:conf/tacas/AmlaM07} % Combining Abstraction Refinement and SAT-Based Model Checking
\cite{DBLP:conf/pldi/BeyerHMR07} % Path invariants
\cite{DBLP:journals/sttt/BeyerHJM07} % The software model checker Blast
\cite{DBLP:conf/vmcai/RybalchenkoS07} % Constraint Solving for Interpolation
\cite{DBLP:conf/cav/Rybalchenko10} % Constraint Solving for Program Verification: Theory and Practice by Example
\cite{DBLP:conf/popl/GuptaPR11} % Predicate abstraction and refinement for verifying multi-threaded programs
\cite{DBLP:conf/aplas/GuptaPR11} % Solving Recursion-Free Horn Clauses over LI+UIF
\cite{DBLP:conf/pepm/SatoUK13} % Towards a scalable software model checker for higher-order

Beautiful interpolants
\cite{DBLP:conf/cav/AlbarghouthiM13}

Disjunctions
\cite{DBLP:conf/cav/RummerHK13}

Non-linear
\cite{DBLP:conf/cav/DaiXZ13}

Qunatifiers
\cite{DBLP:conf/sas/BjornerMR13} % On Solving Universally Quantified Horn Clauses
\cite{DBLP:conf/cav/BeyenePR13}. % Solving Existentially Quantified Horn Clauses

>>>>

One of the most common methods of such abstraction is predicate
abstraction\cite{DBLP:conf/cav/GrafS97} within CounterExample-Guided
Abstraction Refinement (CEGAR) framework
\cite{DBLP:conf/cav/ClarkeGJLV00,DBLP:conf/popl/BallR02,DBLP:conf/popl/HenzingerJMS02}.
An automated theorem prover finds appropriate predicates for every
program location.  An execution states at those locations is then
expressed by a Boolean valuation of the given predicates.  If the
abstraction is too coarse and a model checker discovers an infeasible
error execution path in an abstract system, the prover computes an
additional predicate at those program locations to refine the
abstraction predicates.

In order to obtain an additional abstraction predicate at program
locations along the infeasible counterexample, one class of automated
theorem provers, called an interpolating theorem prover
\cite{DBLP:journals/tcs/McMillan05,DBLP:conf/vmcai/RybalchenkoS07},
computes a separating predicate called an interpolant between two sets
of constraints; the one consists of the constraints from the program
entry point to the location, and the other consists of the constraints
from the location to the program failure.  Those constraints include
variable assignments and assertions to be satisfied originated from
conditional branches.

@@

We incorporated our algorithm to the software model checker for
higher-order programs (MoCHi) \cite{DBLP:conf/pldi/KobayashiSU11}.  It
is specifically designed to verify the correctness of higher-orde
programs written in a small subset of ML.  It infers dependent types
for input higher-order programs \cite{DBLP:conf/ppdp/UnnoK09}.

Our implementation make use of Z3 \cite{DBLP:conf/tacas/MouraB08} as
an SMT solver.

For simplicity of the implementation, we assume that the linear
inequalities in the integer space.  Because of this, our algorithm
lost the completeness.  By using Motzkin's transpose theorem
\cite{DBLP:journals/networks/Rajan90}, it is possible to handle linear
inequalities in both $\mathbf{ax} + b \leq 0$ and $\mathbf{ax} + b <
0$.

@@

Our interpolating theorem prover is used as a sub-procedure to
solve Horn clauses.

\begin{itemize}
\item CSIsat \cite{DBLP:conf/cav/BeyerZM08}
\item FOCI \cite{website:foci}
\item CLP-Prover \cite{website:clp}
\end{itemize}

@@

\chapter{Related work}
\label{chap:related}
\input{related.tex}
